Unions of Balls and Configuration Space

### 2014-08-29 Writing/Final/article.tex
updates

\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, reconnect these retracted points with other ones using their previous connection. By doing so, we got a simple graph that characterize the topology of \emph{C-space}. We would like to call it \emph{Topology Roadmap}. This roadmap can also be used to determine if paths exist between two configurations. An example of such roadmap is shown in Figure \ref{simplifiedgraph}. Filled triangles, along with large balls, are suggesting some large open areas, which is a problem \cite{largeconvex} is trying to address.

>>>>

\indent The second part of this phase can be stated as: retract all connected 2-simplices into one point, while keep check the 1st betti number of these merged 2-simplices, reconnect these retracted points with other ones using their previous connection information. By doing so, we got a simple graph that characterize the topology of \emph{C-space}. We would like to call it \emph{Topology Roadmap}. This roadmap can also be used to determine if paths exist between two configurations. An example of such roadmap is shown in Figure \ref{simplifiedgraph}. Filled triangles, along with large balls, are suggesting some large open areas, which is a problem \cite{largeconvex} is trying to address.
